Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-16 Scripts/Initial_Analysis.Rmd
small test changes

    total <- NULL

@@

# dbem_import(
#   taxon_key <- 600004,
#   iyr <- 1951,
#   fyr <- 1952,
#   data_type <- "Abd",
#   ensamble_list = c(102,103),
#   Path <- DBEM_path
# )

# unique(x$ensamble)
# head(x)

@@

#### For testing 
Spp <- 600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Spp <- 600004 # Argument 1 must have names (RFMO)
# Spp <- 600464 # Discrete species 
# Spp <- 600051 # One of Pierrs massive (wrong) discrete spp
# x <- c(600464, # Discreat spp in one nation
# 600059, # nowhere to be found spp
# 601352, # Discrete spp in two nations
# 600004) # transboundary spp
# Model <- "All"
# Coord <- CoorG
# 
# # For EEZ
# Neighbours <- Neighbours_Data
# Index_Code <- Index_Code

@@

Spp_list <- unique(Transboundary_spp$taxon_key)[3:4]

@@

####_______________________ ####
# Estimating proportion change
####_______________________ ####

# suppressWarnings(
  r_proportion_change <- bind_rows(
    lapply(
      Spp_list, #c(600004,600005),
      EstPropChange,
      iyr <- iyr,
      fyr <- fyr,
      data_type <- "Catch",
      ensamble_list = ensamble_list,
      Path =DBEM_path,
      Neighbours = Neighbours
    )
  )
# )

>>>>

     # total <- NULL

@@

x <- dbem_import(
  taxon_key <- 600004,
  iyr <- 1951,
  fyr <- 1952,
  data_type <- "Catch",
  # ensamble_list = c(102,103),
  ensamble_list =ensamble_list,
  Path <- DBEM_path
)

unique(x$ensamble)
# head(x)

@@

#### For testing 
# Spp <- 600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Spp <- 600004 # Argument 1 must have names (RFMO)
# Spp <- 600464 # Discrete species 
# Spp <- 600051 # One of Pierrs massive (wrong) discrete spp
# x <- c(600464, # Discreat spp in one nation
# 600059, # nowhere to be found spp
# 601352, # Discrete spp in two nations
# 600004) # transboundary spp
# Model <- "All"
# Coord <- CoorG
# 
# # For EEZ
# Neighbours <- Neighbours_Data
# Index_Code <- Index_Code

@@

Spp_list <- unique(Transboundary_spp$taxon_key)[4:5]

@@

# Problema con 600006

####_______________________ ####
# Estimating proportion change
####_______________________ ####
r_proportion_change <- NULL
# suppressWarnings(
  r_proportion_change <- bind_rows(
    lapply(
      Spp_list, #c(600004,600005),
      EstPropChange,
      iyr <- iyr,
      fyr <- fyr,
      data_type <- "Catch",
      ensamble_list = ensamble_list,
      Path =DBEM_path,
      Neighbours = Neighbours
    )
  )
# )
